---
title: "Vignette Title"
author: "J. Doe"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Research Question

A short sentence describing the question central to the analysis.

# Introduction

Explain the purpose of the vignette. Give a brief explanation of the questions
that will be answered and some background information. These vignettes are
written in [Rmarkdown](http://rmarkdown.rstudio.com). You can find [details
about markdown here](http://rmarkdown.rstudio.com/authoring_basics.html) and
[details about code chunks
here](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

This template document in Rmarkdown format is located at 
https://github.com/nescent/popgenInfo/tree/master/TEMPLATE.Rmd.

# Assumptions

All biological analyses have assumptions.

- Assumption 1
- Assumption 2

# Resources

## Data

Links to information about the data if needed e.g. package vignettes. You can
use an [external
link](https://github.com/cran/adegenet/blob/master/inst/files/nancycats.gtx) or
you can place the data [in the `data/` folder](https://github.com/nescent/popgenInfo/blob/master/data/nancycats.gtx)
(please keep this < 200kb).

## Packages

Packages required. Say where these can be found, can link to the list of
packages on our repository page here also.

Loading the required packages:  

```{r, packages, message=FALSE}
library("survival")
```

# Analysis (divided into sections)

Example Sections

## Section 1: Load the data

## Section 2: Exploratory Data analysis/Checking assumptions  
  
## Section 3: Summary statistics  

## Section 4: Visualizing the results

# Conclusions

# Contributors

- Author 1 (Author)
- Author 2 (Author)
- Contributor 1 (role)

# Acknowledgements

Thank you to [@NESCent](https://github.com/NESCent) for providing the 
[template](https://github.com/NESCent/popgenInfo) for this vignette.

# Session Information

This shows us useful information for reproducibility. Of particular importance
are the versions of R and the packages used to create this workflow. It is
considered good practice to record this information with every analysis.

```{r, sessioninfo}
options(width = 100)
devtools::session_info()
```


