---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = TRUE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

For interactive / manual vignette building, setting caching instead to TRUE 
can dramatically speed up the builds, by caching the results of each chunk.

```{r}
knitr::opts_chunk$set(cache=FALSE)
```




# Research Question

A short sentence describing the question central to the analysis.

# Introduction

Explain the purpose of the vignette. Give a brief explanation of the questions
that will be answered and some background information. These vignettes are
written in [Rmarkdown](http://rmarkdown.rstudio.com). You can find [details
about markdown here](http://rmarkdown.rstudio.com/authoring_basics.html) and
[details about code chunks
here](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

# Assumptions

All biological analyses have assumptions.

- Assumption 1
- Assumption 2

# Resources

## Data

Information about the data. 

Note that there are several ways to include data in your package, documented at 
http://r-pkgs.had.co.nz/data.html

# Analysis (divided into sections)

Example Sections

## Section 1: Load the data

## Section 2: Exploratory Data analysis/Checking assumptions  
  
## Section 3: Summary statistics  

## Section 4: Visualizing the results

# Conclusions

# Contributors

- Author 1 (Author)
- Author 2 (Author)
- Contributor 1 (role)

# Acknowledgements

Thank you to [@NESCent](https://github.com/NESCent) for providing the 
[template](https://github.com/NESCent/popgenInfo) for this vignette.

# Session Information

This shows which packages and versions were used for the analysis. Note that under
RStudio "Tools - Project Options" you can select "Packrat" to create a project-specific
library to ensure other analysts will run the exact same version of all packages.

```{r, sessioninfo}
options(width = 100)
devtools::session_info()
```

