---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = TRUE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Preamble

The `ProjectAsPackage` package and this vignette provide a template for generating reproducible analyses as an R package. [Its repo](https://www.github.com/waldronlab/ProjectAsPackage) is set up as a GitHub "template" allowing you to initiate a new repository with it as the starting point for a new analysis.


For interactive / manual vignette building, setting caching instead to TRUE 
can dramatically speed up the builds, by caching the results of each chunk. The caching line is not shown in output because of the option `echo=FALSE`. 

```{r, echo=FALSE}
knitr::opts_chunk$set(cache=FALSE)
```

# Research Question

A short sentence describing the question central to the analysis.

# Introduction

Explain the purpose of the vignette. Give a brief explanation of the questions
that will be answered and some background information. These vignettes are
written in [Rmarkdown](http://rmarkdown.rstudio.com). You can find [details
about markdown here](http://rmarkdown.rstudio.com/authoring_basics.html) and
[details about code chunks
here](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

# Assumptions

All biological analyses have assumptions.

- Assumption 1
- Assumption 2

# Resources

## Data

Information about the data. 

Note that there are several ways to include data in your package, documented at 
http://r-pkgs.had.co.nz/data.html

**ProjectAsPackage** demonstrates two ways:
1. as a prepared R object (in this case `data.frame`) prepared and stored as `data/gardasil.rda`in the package's directory and documented in the file `R/gardasil.R`.
2. as a *.csv* file `inst/extdata/gardasil.csv`

# Analysis (divided into sections)

Example Sections

## Section 1: Load the data

## Section 2: Exploratory Data analysis/Checking assumptions  
  
## Section 3: Summary statistics  

## Section 4: Visualizing the results

# Conclusions

# Contributors

- Author 1 (Author)
- Author 2 (Author)
- Contributor 1 (role)

# Acknowledgements

Thank you to [@NESCent](https://github.com/NESCent) for providing the 
[template](https://github.com/NESCent/popgenInfo) for this vignette.

# Session Information

This shows which packages and versions were used for the analysis. Note that under
RStudio "Tools - Project Options" you can select "Packrat" to create a project-specific
library to ensure other analysts will run the exact same version of all packages.

```{r, sessioninfo}
options(width = 100)
devtools::session_info()
```

